S2 pioneer factor MS

### 2022-09-23 manuscript/manuscript.Rmd
update figure titles and add fig 3

| Reagent                            | Source/vendor            | Catalog/accession \# |
|----------------------------|------------------------|--------------------|
| pMT-puro                           | AddGene                  | 17923                |
| Gibson Cloning                     | New England Biolabs      | E2611                |
| Schneider's Medium                 | Thermo Fisher Scientific | 21720001             |
| Fetal Bovine Serum                 | Omega Scientific         | FB-02                |
| Antibiotic/antimycotic             | Thermo Fisher Scientific | 15240062             |
| Effectene Transfection Reagent     | Qiagen                   | 301427               |
| PVDF Membrane                      |                          |                      |
| **Antibodies**                     |                          |                      |
| Anti-Zld                           | Harrison et al., 2010    |                      |
| Anti-Grh                           | Harrison et al., 2010    |                      |
| Anti-Twi                           | He et al., 2015          |                      |
| Anti-HA-peroxidase clone 3F10      | Roche                    | 12013819001          |
| Anti-Tubulin DM1A                  | Sigma                    | T6199-200UL          |
| goat anti-rabbit IgG-HRP conjugate | Bio-Rad                  | 1706515              |
| Anti-HA clone 12CA5                |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |

@@

**Figure 2: Twist binds closed chromatin extensively and drives accessibility at some sites.**

**Figure 3: Some endogenous targets are resistant to binding by ectopic pioneer factors.**

**Figure 4: Binding and opening of closed chromatin is concentration dependent.**

**Figure 5: H3K27me3 and H3K9me3 are barriers to pioneer-factor binding.**

>>>>

| Reagent                            | Source/vendor            | Catalog/accession \# |
|------------------------------------|--------------------------|----------------------|
| pMT-puro                           | AddGene                  | 17923                |
| Gibson Cloning                     | New England Biolabs      | E2611                |
| Schneider's Medium                 | Thermo Fisher Scientific | 21720001             |
| Fetal Bovine Serum                 | Omega Scientific         | FB-02                |
| Antibiotic/antimycotic             | Thermo Fisher Scientific | 15240062             |
| Effectene Transfection Reagent     | Qiagen                   | 301427               |
| PVDF Membrane                      |                          |                      |
| **Antibodies**                     |                          |                      |
| Anti-Zld                           | Harrison et al., 2010    |                      |
| Anti-Grh                           | Harrison et al., 2010    |                      |
| Anti-Twi                           | He et al., 2015          |                      |
| Anti-HA-peroxidase clone 3F10      | Roche                    | 12013819001          |
| Anti-Tubulin DM1A                  | Sigma                    | T6199-200UL          |
| goat anti-rabbit IgG-HRP conjugate | Bio-Rad                  | 1706515              |
| Anti-HA clone 12CA5                |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |
|                                    |                          |                      |

@@

**Figure 2: Twist binds closed chromatin extensively and drives accessibility at a limited number of sites.**

**Figure 3: Motif content shapes pioneer-factor activity**

**Figure 4: H3K27me3 and H3K9me3 are barriers to pioneer-factor binding.**

**Figure 5: Binding and opening of closed chromatin is concentration dependent.**
